
\section{Scope}

This Working Group is to review the \gls{DM} \gls{provenance} based on what is now
available in butler gen 3 and the DPPDized data model.

 Ideally this working group would convene and finish before the end of 2019.

\section{Responsibilities}

The Working Group (\gls{WG}) has the following responsibilities:

\begin{itemize}
    \item Asses available \gls{provenance} information in the current gen3 butler \gls{metadata} registry
    \item Identify \gls{provenance} gaps in the data model and how they should be filled.
    \item Classify the resulting \gls{provenance} needs as critical (needed for commissioning), important (need for full ops) or nice to have.
\end{itemize}

This group is not intended to solve how missing \gls{provenance} information should be added - this should fall the middleware group.
This group may of course suggest ways to gather/store such \gls{provenance} information.

\section{Specific Tasks}

\subsection{ Asses Available Information}

This may have to be provided by the Middleware group based on he gen3 runs of \gls{HSC} processing and the
resulting data model.

\subsection{Identify Gaps and needs}
The group should then identify use cases e.g' " can I find which PVIs used this \gls{calibration} file " and determine if they can be answered with the existing \gls{metadata}. This will obviously be best facilitated by someone very familiar with gen 3 butler.

In general the list of \gls{provenance} requirement or  "use cases"  is the most important output of this group.
\subsection{Classify use cases}
The identified use cases need to be classified and that classification has to be agreed within \gls{DM} - hence it may need to be in a formal document.



\section{Membership}

The proposed membership is:

\begin{itemize}
    \item Simon Krughoff
    \item Robert Gruendl
    \item Gregory Dubois Felsmann
    \item Amanda Bauer (\gls{EPO} Tucson )
    \item Somone from commisiioinng verification (Keith?)
\end{itemize}


\section{Reporting}

The \gls{WG} Chair shall report directly to the \gls{DM} Project manager weekly.
